Reference label transfer of the fetal kidney reference (Stewart et al.) for `r params$sample_id`

### 2024-11-20 analyses/cell-type-wilms-tumor-06/notebook_template/00b_characterize_fetal_kidney_reference_Stewart.Rmd

---
title: "Characterize the fetal kidney reference from the kidney cell atlas"
author: "Maud PLASCHKA"
date: '2024-08-07'
params:
  padj_threshold: 0.05
  lfc_threshold: 1
  rate1_threshold: 0.5
  seed: 12345
  fetal_kidney_path: "../scratch/fetal_kidney.rds"
output: 
  html_document: 
    toc: yes
    toc_float: yes
    code_folding: hide
    highlight: pygments
    df_print: paged
    self_contained: yes
    mode: selfcontained
---

@@

The aim is to characterize the human fetal kidney from the kidney cell atlas.
You can find more about the human kidney atlas here: https://www.kidneycellatlas.org/ [1]
The rds data can be download using the download link: <https://datasets.cellxgene.cziscience.com/40ebb8e4-1a25-4a33-b8ff-02d1156e4e9b.rds>.
The reference was downloaded and created in the script `scripts/prepare-fetal-references.R`.

>>>>

---
title: "Characterize the fetal kidney reference from the kidney cell atlas"
author: "Maud PLASCHKA"
date: '2024-08-07'
params:
  padj_threshold: 0.05
  lfc_threshold: 1
  rate1_threshold: 0.5
  seed: 12345
  fetal_kidney_path: "../scratch/fetal_kidney_seurat.rds"
output:
  html_document:
    toc: yes
    toc_float: yes
    code_folding: hide
    highlight: pygments
    df_print: paged
    self_contained: yes
    mode: selfcontained
---

@@

The aim is to characterize the human fetal kidney from the kidney cell atlas obtained from CELLxGENE.
You can find more about the human kidney atlas here: https://www.kidneycellatlas.org/ [1].
The reference was downloaded and created in the script `scripts/prepare-fetal-references.R`.

### 2024-11-20 analyses/cell-type-wilms-tumor-06/notebook_template/02b_label-transfer_fetal_kidney_reference_Stewart.Rmd

---
title: "Reference label transfer of the fetal kidney reference (Stewart et al.) for `r params$sample_id`"
author: "Maud PLASCHKA"
date: '2024-08-13'
params:
  scpca_project_id: "SCPCP000006"
  sample_id: "SCPCS000176"
  seed: 12345
  homologs_file: "../scratch/homologs.rds"
  testing: 0
output: 
  html_document: 
    toc: yes
    toc_float: yes
    code_folding: hide
    highlight: pygments
    df_print: paged
---

@@

# prepare the query for label transfer
# we don't want to overwrite the srat object since `prepare_query`
#  removes features that are not present in the reference
DefaultAssay(srat) <- srat_assay
query <- prepare_query(
  srat,
  rownames(reference),
  srat_assay,
  params$homologs_file
)
```

>>>>

---
title: "Reference label transfer of the fetal kidney reference (Stewart et al.) for `r params$sample_id`"
author: "Maud PLASCHKA"
date: '2024-08-13'
params:
  scpca_project_id: "SCPCP000006"
  sample_id: "SCPCS000176"
  seed: 12345
  testing: 0
output: 
  html_document: 
    toc: yes
    toc_float: yes
    code_folding: hide
    highlight: pygments
    df_print: paged
---

@@

# prepare the query for label transfer
# we don't want to overwrite the srat object since `prepare_query`
#  removes features that are not present in the reference
DefaultAssay(srat) <- srat_assay
query <- prepare_query(
  srat,
  rownames(reference),
  srat_assay,
  convert_gene_names = FALSE
)
```
